Machine Learning guided workflow for Ribosome Binding Site engineering

### 2021-05-12 paper/supplementary.tex

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.25]{plots/Supplementary/Structure GGGGGG.pdf}
         \caption{$y=x$}
         \label{fig:GGGGGG}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.25]{plots/Supplementary/Structure GGGGGC.pdf}
         \caption{$y=3sinx$}
         \label{fig:GGGGGC}
     \end{subfigure}
     \vskip\baselineskip
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.25]{plots/Supplementary/Structure CGGGAC.pdf}
         \caption{$y=5/x$}
         \label{fig:CGGGAC}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.25]{plots/Supplementary/Structure CACGTT.pdf}
         \caption{$y=5/x$}
         \label{fig:CACGTT}
     \end{subfigure}
        \caption{\textbf{Folding predictionds for four different RBS.} Here we show the predicted, energetically most favourable structures for four of our RBS with the following cores: GGGGGG, GGGGGC, CGGGAC, CACGTT and their immediate upstream and downstream background sequence. There is no discerbile and consistent difference between strong ones (the first two) and weak ones (the last two).}
        \label{fig:structures}
\end{figure}

>>>>

\begin{figure}
     \centering
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.25]{plots/Supplementary/Structure_GGGGGG.pdf}
         \caption{$y=x$}
         \label{fig:GGGGGG}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.25]{plots/Supplementary/Structure_GGGGGC.pdf}
         \caption{$y=3sinx$}
         \label{fig:GGGGGC}
     \end{subfigure}
     \vskip\baselineskip
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.25]{plots/Supplementary/Structure_CGGGAC.pdf}
         \caption{$y=5/x$}
         \label{fig:CGGGAC}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.49\textwidth}
         \centering
         \includegraphics[scale=0.25]{plots/Supplementary/Structure_CACGTT.pdf}
         \caption{$y=5/x$}
         \label{fig:CACGTT}
     \end{subfigure}
        \caption{\textbf{Folding predictionds for four different RBS.} Here we show the predicted, energetically most favourable structures for four of our RBS with the following cores: GGGGGG, GGGGGC, CGGGAC, CACGTT and their immediate upstream and downstream background sequence. There is no discerbile and consistent difference between strong ones (the first two) and weak ones (the last two).}
        \label{fig:structures}
\end{figure}

\input{paper/mixture_absGau}
